Automated Essay Scoring

### 2018-05-10 paper/acl17-latex/paper.tex
Added new paragraph in introduction

There is a recent surge in use of deep learning for the task of automated essay scoring.
These models have shown to out perform the traditional models based on hand coded features
and currently have the state of art performance in this task. The current state of art model
is from Taghipour et al. \cite{nea}

>>>>

There is a recent surge in use of deep learning for the task of automated essay scoring.
These models have shown to out perform the traditional models based on hand coded features
and currently have the state of art performance in this task. The current state of art model
is from Taghipour et al. \cite{nea} and the state of art non-neural model is EASE \cite{ease}.
In this paper we explore the performance of deep-learning based systems on real life scenarios. We try to see if their performance is actually better than traditional non-neural based models in qualitative sense.

Essay writing is usually a part of the student assessment  process.    Several  organizations,  such  as Educational Testing Service (ETS)\cite{ets}, evaluate the writing skills of students in their examinations. Because of the large number of  students participating in these exams, grading all essays is very time-consuming. Thus, some organizations have been using AES systems to reduce the time and cost of scoring essays. Therefore, it is of prime importance that we understand the metrics that these new models are actually using to score the essays.
